


% 1/ Education
\tbfpart{Education}
\begin{yearlist}
\item[Master Degree of Astronomy]{2011 -- 2013}
	{PUC, Santiago, Chile}
    {One of the two best Chilean Universities. 
    Chile is a leader country in Astrophysics.}

\item[Engineer Degree]{2008 -- 2011}
	{Ecole Polytechnique, Paris, France}
    {One of France's prominent universities for hight-­level scientific training.}


\item[Preparatory School]{2006 -- 2008}
	{Lyc\'ee Victor Grignard, Cherbourg, France}
	{Preparatory years for the nationwide competitive examination to the elite French Grandes Ecoles for scientific studies.  }


\item[Baccalaur\'eat]{2003 -- 2005}
	{Lyc\'ee Victor Grignard, Cherbourg, France}
	{Baccalaur\'at S\'erie S French Secondary School Diploma in Mathematics and Physics. 
    Diploma awarded with High Honours.}

\end{yearlist}


% 2/ Job
\tbfpart{Work experience}
\begin{joblist}

\item[Astronomer]{2013}
	{ESO, Santiago, Chile}
	{Development of a Python GUI software to measure image quality.}


\item[Commandos Marine]{2008 -- 2009}
	{Military base, Lorient, France}
	{Eight ­month leadership training, a part of the school curriculum}

\item[Ostreiculture]{2006 -- 2008}
	{St Vast la Houge, France}
	{Farmer work consisting of returning oyster webs during low tide.}


\item[Counsellor]{2006 -- 2008}
	{Summer camps}
	{Counsellor in charge of 3 to 10 or 10 to 16 years old children.}
\end{joblist}


% 3/ Skill
\tbfpart{Skills}

\tbfskilltwo{Languages}{
	\begin{languagelist}
	\item{French} 	{mother tongue}
	\item{Spanish} 	{bilingual}
	\item{English} 	{fluent} 
	\end{languagelist}
}

\tbfskilltwo{Softwares}{
		Java,
		C++, 
		Python, 
		BaSh, 
		IRAF, 
		Assembly (x86, ARM), 
		Vim, 
		\LaTeX
	}

\tbfskilltwo{Activities}{
	Swim, Bike, Climb, Sky-dive
}
